\thispagestyle{empty} % Removes page numbers for the dedication page

\begin{itshape}
\raggedright

\noindent \textbf{\large To my late father,} \\
\vspace{0.5em}
\hspace{1.5em} You may not be here to see me reach this milestone, but I know you are looking down with pride and love. Your sacrifices were not in vain, and I am forever grateful to you for instilling in me the values of hard work, perseverance, and dedication. While it pains me that you are not by my side today, I hope this achievement serves as a tribute to your memory and the legacy you left behind. I miss your presence every day, and I will always carry your wisdom in my heart as I continue my pursuit of knowledge.

\vspace{2em}

\noindent \textbf{\large To my mother,} \\
\vspace{0.5em}
\hspace{1.5em} Thank you deeply for your endless sacrifices to maintain the same loving environment for us, just as if my father were still here with us. Your spirit and resilience inspire me to keep striving for higher achievements. I wish to express my deepest gratitude, but words will never be enough; I will keep pushing forward to honor even a fraction of everything you have done for me.

\vspace{2em}

\noindent \textbf{\large To my brothers,} \\
\vspace{0.5em}
\hspace{1.5em} Thanks to my older brother and my twin brother for the daily encouragement and laughs you both gave me. The passion and support you both show consistently is truly rare. Thank you again for always believing in me.

\vspace{2em}

\noindent \textbf{\large To my friends,} \\
\vspace{0.5em}
\hspace{1.5em} A huge thank you to all my friends. I apologize for not naming each of you individually here, but I am incredibly grateful for your companionship and motivating words. I am truly blessed to have such a supportive group of friends standing by my side every step of the way.

\begin{center}
    \vspace*{1em}
    {\large ``The secret\phantom{c}of harvest and greatest\phantom{c}enjoyment of existence is:\phantom{c}to live dangerously! Build\phantom{c}your cities on the\phantom{c}slopes of Vesuvius!''} \\    \vspace{0.5em}
    \small --- Friedrich Nietzsche
    \vspace*{2em}
\end{center}
\vfill

\begin{flushright}
    \textbf{\Large Fares}\\
    \vspace{0.3em}
    \textbf{\Large Chams Edin}
\end{flushright}

\end{itshape}