\thispagestyle{empty} % Removes page numbers for the dedication page

\begin{itshape}
\raggedright

\noindent \textbf{\large To my beloved parents,} \\
\vspace{0.5em}
\hspace{1.5em}Words that describe how much you mean to me have eluded me for many years and still escape me, as what you mean to me goes beyond the boundaries of any possible sentence. You believed in me even during those times when I did not believe in myself; you never hesitated to give me more than your own share so that I can move forward freely. Every step I take toward success starts with you.
    I do not seek grandeur in this world. I do not pursue recognition or fame. All I wish to achieve in this world is to have you happy with me; to bring smiles to your face again and again — smiles which were always my source of strength, the reason why I have kept moving ahead with confidence. Nothing else does matter; nothing matters as long as you bless me. It's your blessings that make me brave enough to accomplish great things. It's your blessings that give meaning to my life. I hope from the depths of my heart to always deserve your trust.
    This book is dedicated to you, from the bottom of my heart.

\vspace{2em}

\noindent \textbf{\large To my brothers,} \\
\vspace{0.5em}
\hspace{1.5em}There are some individuals who end up coming into your life simply by accident, and it so happens that you have come into my life even before I had any say in the matter, and I am really thankful for that. You have seen all the variations of myself, both when I was sure of myself and lost; at times when I felt extremely strong and at times when I was completely tired, and you never made me feel like any one of the versions was ever insufficient.

\vspace{2em}

\noindent \textbf{\large To my friends,} \\
\vspace{0.5em}
\hspace{1.5em}There was never any question that you would show up because you always did, without fail, every single time. This adventure was not one without its share of tough days, but somehow, you seemed to know the right way to lighten them by simply being there. It was your sense of humor on the days when we really needed a good laugh, and your patience during those times that required even more. In reflecting now, it strikes me how much of this process your friendship carried me through all alone. I don’t say thank you often enough, but I really mean it this is not taken for granted by me.


\vfill

\begin{flushright}
    \textbf{\Large Ben Zekri}\\
    \vspace{0.5em}
    \textbf{\Large Wajih}
\end{flushright}

\end{itshape}
