\begingroup
    % Paragraph indentation and spacing
    \setlength{\parindent}{1.5em}
    \setlength{\parskip}{0.8\baselineskip}
    % Custom star bullet (slightly larger)
    \renewcommand{\labelitemi}{\large $*$}
\hspace{1.5em} The exponential rise of cloud computing, hyperscale operations, and AI has completely revolutionized what infrastructure looks like today. AI platform, from distributed training to real-time inference, drive network requirements that are an order of magnitude beyond traditional enterprise applications. Data centers have moved from simple storage repositories to becoming the engines of the digital economy, where network scalability is now the determining factor of infrastructure success and failure.

The traditional three-tier architecture is rapidly becoming obsolete, unable to effectively address East-West traffic and mobility requirements of AI-based applications and services. Inefficiencies such as Spanning Tree's bandwidth waste, unstable Layer 2 domains, and site boundaries are becoming major bottlenecks for virtual machine mobility and multi-tenancy. For a national operator such as Tunisie Telecom, these are not just conceptual limitations, but real-world inhibitors of network scalability and reliability in critical telecommunications infrastructure.

This project is designed to deploy a BGP EVPN-VXLAN IP Fabric across various data centers using Cisco Nexus 9000 switches and the Nexus Dashboard Fabric Controller (NDFC) product. This new approach to the legacy architecture is designed to overcome the limitations of VM mobility, Layer 2 extension, and tenancy for Tunisie Telecom. In the end, it provides a fabric that is suitable for future AI-driven applications without the need for further fundamental changes.

This report is assembled into five chapters:
\begin{itemize}
    \item \textbf{Chapter 1:} Introduces Tunisie Telecom as the host organization, establishes the technical and operational context of the project.
    \item \textbf{Chapter 2:} Builds the theoretical foundation of the project.
    \item \textbf{Chapter 3:} Examines the evolution of network automation, establishes the case for infrastructure programmability at scale.
    \item \textbf{Chapter 4:} Presents the complete multi-site IP Fabric architecture.
    \item \textbf{Chapter 5:} Covers the full deployment of the solution within an EVE-NG emulation environment.
\end{itemize}

The work presented here is not an academic exercise but a concrete response to the infrastructure challenges facing one of Tunisia's most critical telecommunications operators.
\endgroup