\chapter*{General Conclusion}
\addcontentsline{toc}{chapter}{General Conclusion}

\begingroup
\setlength{\parindent}{1.5em}
\setlength{\parskip}{0.8\baselineskip}

\hspace{1.5em}The problem this project tackled was the
incapacity of Tunisie Telecom to run modern virtualized,
multi-site, and AI-based workloads using a traditional
three-tier data center network. The solution is a BGP
EVPN-VXLAN IP Fabric deployed across two sites,
consisting of Cisco Nexus 9000 and automation using
NDFC.

Chapter 2 explained how OSPF underlay, BGP EVPN
control plane, and VXLAN encapsulation solve all the
problems in the legacy architecture. Chapter 3 described
how to implement this into a multi-site Spine-Leaf
fabric with Border Gateway Leaf and WAN links using
NDFC. Finally, Chapter 4 tested eight cases: ECMP solved
STP inefficiency, EVPN mitigated broadcast storms,
ARP suppression addressed unnecessary broadcasting, MAC
Mobility facilitated cross-site VM migration, Type-5
routes optimized inter-site L3 traffic, VRF isolation
outperformed VLAN limitations, NDFC obviated manual
configuration, and BFD ensured spine node failure
restoration under one second.

Technical achievements aside, this project offers a
flexible infrastructure for Tunisie Telecom's digital
transformation. Leaf devices get provisioned using NDFC
POAP, segment tenants in seconds via MSD, and new sites
can join without redesign.

Next steps for future projects include NSX-T
integration for micro-segmentation, an end-to-end
SD-WAN fabric for application-aware path selection,
IDS/IPS service nodes for improved east-west security,
and automated remediation within NDFC compliance rules.
\endgroup